### 2021-02-17 evaluation.tex
Add a todo

Since the \gls{tkbo} never compares a predicate symbol with a function symbol,
two separate precedences can be considered for each problem:
a predicate precedence and a function precedence.
We trained a predicate precedence recommender separately from a function precedence recommender
to simplify the training process and to isolate the effects of the predicate and function precedences.
\todo{FB: Weak, handwavy spot. Consider improving the argumentation. MS: tady activum dokonce pomuze 
stim weak spotem. "A recommender is trained separately, because" zni trochu jako "autorita predepisuje delate to prave takto,
protoze <dobre duvody>". Kdyz reknes "we trained, because", ty duvodu uz mohou byt pouze prakticke a ctenar to pochopi! }
This section describes how the training data for training a \emph{predicate} precedence recommender was generated.
Training data for training a function precedence recommender was generated analogously.
\todo{MS: taky jsem to hodil do minuleho casu. Myslim, ze to je opet blizsi skutecnosti: V Cestine:
"Takhle jsme to delali" (at vite, co presne kritizovat) vs "Takhle se to dela" (kritika pak muze byt o dost silnejsi,
protoze jakoby tvrdis, ze prezentujes spravnou metodiku).}

>>>>

Since the \gls{tkbo} never compares a predicate symbol with a function symbol,
\todo{FB: Consider referencing an earlier section that explains KBO or TKBO.}
two separate precedences can be considered for each problem:
a predicate precedence and a function precedence.
We trained a predicate precedence recommender separately from a function precedence recommender
to simplify the training process and to isolate the effects of the predicate and function precedences.
\todo{FB: Weak, handwavy spot. Consider improving the argumentation. MS: tady activum dokonce pomuze 
stim weak spotem. "A recommender is trained separately, because" zni trochu jako "autorita predepisuje delate to prave takto,
protoze <dobre duvody>". Kdyz reknes "we trained, because", ty duvodu uz mohou byt pouze prakticke a ctenar to pochopi! }
This section describes how the training data for training a \emph{predicate} precedence recommender was generated.
Training data for training a function precedence recommender was generated analogously.
\todo{MS: taky jsem to hodil do minuleho casu. Myslim, ze to je opet blizsi skutecnosti: V Cestine:
"Takhle jsme to delali" (at vite, co presne kritizovat) vs "Takhle se to dela" (kritika pak muze byt o dost silnejsi,
protoze jakoby tvrdis, ze prezentujes spravnou metodiku).}
